Manuscript Figures

### 2018-06-08 Manuscript Figures.Rmd
Higher quality exports of figures

```{r extra4, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=4, fig.height=4, fig.align='center'}
# Average expression for genes in each subgenome, biased by sample size.  While other plots show that maize1 dominates maize2 more often in all tissue, maize2 
# for pollen and endosperm crown the average expression is higher in maize2.  Basically, when maize2 wins, it wins by more raw FPKMs.  If we account for all
# genes in the subgenome, not just the pairs, maize2 often has higher average expression.  This is probably due to many very low expressed genes in maize1.
data <- 
  homeologs.pairs %>%
  # subset(Maize1 != "" & Maize2 != "") %>% #only matching
  # subset(!(Maize1 %in% c("") & Maize2 %in% c(""))) %>% #only nonmatching
  distinct() %>%
  select(Maize1, Maize2) %>%
  left_join(maize.walley.v4mapped.expression, by=c("Maize1"="geneID")) %>%
  rename(FPKM_avg1=FPKM_avg) %>%
  left_join(maize.walley.v4mapped.expression, by=c("Maize2"="geneID", "sample"="sample")) %>%
  rename(FPKM_avg2=FPKM_avg) %>%
  select(Maize1, Maize2, sample, FPKM_avg1, FPKM_avg2) %>%
  # subset(sample %in% c("B73 Mature Pollen")) %>%
  group_by(sample) %>%
  summarize(Mean1=mean(FPKM_avg1, na.rm=TRUE), Mean2=mean(FPKM_avg2, na.rm=TRUE))
data <- 
  data %>%
  gather(subgenome, FPKM, -1)

@@

```{r print, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=8, fig.height=8, fig.align='center'}
# ggsave("Output/Figure 1a.png", plot = chromosome_plot_exp)
# ggsave("Output/Figure 1b.png", plot = chromosome_plot_abundance)
# 
# png("Output/Figure 2a.png");
# grid.draw(GOTerms_by_subgenome_a)
# dev.off()
# png("Output/Figure 2b.png");
# grid.draw(GOTerms_by_subgenome_b)
# dev.off()
# 
# ggsave("Output/Figure 3.png", plot = subgenome_isoforms_scatter)
# ggsave("Output/Figure 4.png", plot = subgenome_expression_scatter_rep)
# ggsave("Output/Figure 5.png", plot = subgenome_protein_scatter_rep)
# ggsave("Output/Figure 6.png", plot = subgenome_expression_protein_foldchange_scatter)
# ggsave("Output/Figure 7.png", plot = subgenome_expression_protein_scatter)
# ggsave("Output/Figure 8.png", plot = subgenome_expression_protein_scatter_rep)
# ggsave("Output/Figure S1.png", plot = subgenome_expression_scatter)
# ggsave("Output/Figure S2.png", plot = subgenome_protein_scatter)
# ggsave("Output/Figure S3.png", plot = subgenome_expression_protein_scatter)
```

>>>>

```{r extra4, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=8, fig.height=8, fig.align='center'}
# Average expression for genes in each subgenome, biased by sample size.  While other plots show that maize1 dominates maize2 more often in all tissue, maize2 
# for pollen and endosperm crown the average expression is higher in maize2.  Basically, when maize2 wins, it wins by more raw FPKMs.  If we account for all
# genes in the subgenome, not just the pairs, maize2 often has higher average expression.  This is probably due to many very low expressed genes in maize1.
data <- 
  homeologs.pairs %>%
  subset(Maize1 != "" & Maize2 != "") %>% #only matching
  # subset(!(Maize1 %in% c("") & Maize2 %in% c(""))) %>% #only nonmatching
  distinct() %>%
  select(Maize1, Maize2) %>%
  left_join(maize.walley.v4mapped.expression, by=c("Maize1"="geneID")) %>%
  rename(FPKM_avg1=FPKM_avg) %>%
  left_join(maize.walley.v4mapped.expression, by=c("Maize2"="geneID", "sample"="sample")) %>%
  rename(FPKM_avg2=FPKM_avg) %>%
  select(Maize1, Maize2, sample, FPKM_avg1, FPKM_avg2) %>%
  # subset(sample %in% c("B73 Mature Pollen")) %>%
  group_by(sample) %>%
  summarize(Mean1=mean(FPKM_avg1, na.rm=TRUE), Mean2=mean(FPKM_avg2, na.rm=TRUE))
data <- 
  data %>%
  gather(subgenome, FPKM, -1)

@@

```{r print, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=8, fig.height=8, fig.align='center'}
# # ggsave("Output/Figure 1a.png", plot = chromosome_plot_exp)
# png(filename = "Output/Figure 1a.png", type = "cairo", units = "in", width = 8, height = 8, pointsize = 12, res = 96)
# plot(chromosome_plot_exp)
# dev.off()
# 
# # ggsave("Output/Figure 1b.png", plot = chromosome_plot_abundance)
# png(filename = "Output/Figure 1b.png", type = "cairo", units = "in", width = 8, height = 8, pointsize = 12, res = 96)
# plot(chromosome_plot_abundance)
# dev.off()
# 
# png("Output/Figure 2a.png");
# grid.draw(GOTerms_by_subgenome_a)
# dev.off()
# png("Output/Figure 2b.png");
# grid.draw(GOTerms_by_subgenome_b)
# dev.off()
# 
# # ggsave("Output/Figure 3.png", plot = subgenome_isoforms_scatter)
# png(filename = "Output/Figure 3.png", type = "cairo", units = "in", width = 8, height = 8, pointsize = 12, res = 96)
# plot(subgenome_isoforms_scatter)
# dev.off()
# 
# # ggsave("Output/Figure 4.png", plot = subgenome_expression_scatter_rep)
# png(filename = "Output/Figure 4.png", type = "cairo", units = "in", width = 12, height = 4, pointsize = 12, res = 96)
# plot(subgenome_expression_scatter_rep)
# dev.off()
# 
# # ggsave("Output/Figure 5.png", plot = subgenome_protein_scatter_rep)
# png(filename = "Output/Figure 5.png", type = "cairo", units = "in", width = 12, height = 4, pointsize = 12, res = 96)
# plot(subgenome_protein_scatter_rep)
# dev.off()
# 
# # ggsave("Output/Figure 6.png", plot = subgenome_expression_protein_scatter_rep)
# png(filename = "Output/Figure 6.png", type = "cairo", units = "in", width = 12, height = 4, pointsize = 12, res = 96)
# plot(subgenome_expression_protein_scatter_rep)
# dev.off()
# 
# ggsave("Output/Figure S1.png", plot = subgenome_expression_scatter)
# ggsave("Output/Figure S2.png", plot = subgenome_protein_scatter)
# ggsave("Output/Figure S3.png", plot = subgenome_expression_protein_scatter)
# ggsave("Output/Figure S4.png", plot = subgenome_expression_protein_foldchange_scatter)
```
